### 2014-05-12 paper.tex
Adding first attempt at paper

\documentclass[a4paper,11pt]{article}
\usepackage{sobrapo-template}
\usepackage[brazil]{babel}
\usepackage[latin1]{inputenc}
\usepackage{amsmath,amssymb}

\usepackage{indentfirst}

\title{An Incomplete Overview of some Applications of Game Theory to Patient Flow}

\begin{document}

\maketitle

\author{
\name{Vincent Knight}
\institute{Cardiff University}
\iaddress{Cardiff, UK}
\email{knightva@cf.ac.uk}
}

\author{
\name{Paul Harper}
\institute{Cardiff University}
\iaddress{Cardiff, UK}
\email{harper@cf.ac.uk}
}

\author{
\name{Jeff Griffiths}
\institute{Cardiff University}
\iaddress{Cardiff, UK}
\email{griffiths@cf.ac.uk}
}

\author{
\name{Izabela Komenda}
\institute{Cardiff University}
\iaddress{Cardiff, UK}
\email{komendai@cf.ac.uk}
}

\vspace{8mm}

\begin{abstract}
Describe paper.
\end{abstract}

\bigskip
\begin{keywords}
Patient Flow, Game Theory, Queueing Theory

\bigskip
\noindent{Main Area: Healthcare}
\end{keywords}

\newpage

\section{Introduction}

\begin{itemize}
    \item Review GT in HC in general (small);
    \item Review congestion type games;
    \item PoA;
    \item Structure.
\end{itemize}

\section{Choosing queues}

\begin{itemize}
    \item PoA in healthcare paper;
    \item Rob's work
\end{itemize}

\section{CCU Work}

\begin{itemize}
    \item IK Paper
\end{itemize}

\section{EU and EMV Interface}

\begin{itemize}
    \item Describe model;
    \item Show some results.
\end{itemize}

\section{Conclusions}

\bigskip
\noindent{\bf Refer\^encias}

\noindent \textbf {Anna, A.} (1996), Comunica\c c\~ao, \textit{Atas do XXVIII SBPO}, 123-134.

\noindent \textbf{Gates, B.}, \textit{Um Livro Muito Bom}, Editor, Local, 2003.

\noindent  \textbf{Pel\'e, E. N. e Rom\'ario, R. R.}, Exemplo de artigo em livro, em Windows, P. T. e Linux, V. G. (Eds.),
\textit{Colet\^ania de Artigos},  Editor, Local, 123-133, 2004.

\noindent  \textbf{Silva, A. B., Souza, C. D. e Santos, E. F.}, T\'\i tulo de um relat\'orio t\'ecnico dispon\'\i vel na Internet,
\textit{ Relat\'orios de Pesquisa em Engenharia de Produ\c c\~ao}, n. 4,  Universidade Z,
1999

\noindent{(www.universidade.br/rel, 4, 2001.}

\noindent  \textbf{Smith, S. e Jones, J.} (2002), A paper on Operations Research, \textit{Pesquisa Operacional},
32, 5-44.

\end{document}

### 2014-05-12 paper.tex
Thrown stuff from PoA paper

@@
 
-\usepackage{indentfirst}
+\usepackage{tikz}
+\usepackage{parskip}
 
@@
 
+\author{
+\name{Rob Shone}
+\institute{Cardiff University}
+\iaddress{Cardiff, UK}
+\email{shoner@cf.ac.uk}
+}
+
 \vspace{8mm}
@@
 
-\begin{itemize}
-    \item PoA in healthcare paper;
-    \item Rob's work
-\end{itemize}
+This section describes how patient choices between various congestion affected services may be modelled.
+In particular the situation shown diagrammatically in Figure \ref{fig:choices} is considered: patients have a choice amongst $M/M/c$ queues.
+
+\begin{figure}[!hbtp]
+Show diagram.
+\end{figure}
+
+There are two approaches to solving this problem: assuming that patients observe or not the system states before choosing a facility.
+A rigorous comparison of these two approaches for individuals choosing to join an $M/M/1$ queue is given in \cite{}.
+
+An unobservable study is given in \cite{} where routing games \cite{Rouhgharden} are used to study the system described.
+The routing game used is shown in \ref{fig:routinggame}.
+
+\begin{figure}[!hbtp]
+Show routing game image.
+\end{figure}
+
+It can be shown that the cost for any given flow $\lambda$ (denoting the amount of traffic from source $i$ to facility $j$) corresponds to...
+
+\begin{equation}
+C(\lambda)=\sum_{i=1}^m\alpha_i\sum_{j}^nd_{ij}\lambda_{ij}+\sum_{j=1}^n\sum_{i=1}^m\lambda_{ij}w_j\left(\sum_{i=1}^m\lambda_{ij}\right)+\sum_{i=1}^m\beta_i\left(\Lambda_i-\sum_{j=1}^n\lambda_{ij}\right)
+\label{C}\end{equation}
+
+Obtaining the Nash flow: ie the equilibrium behaviour.
+
+\begin{equation}
+\Phi(\lambda)=\sum_{i=1}^m\alpha_i\sum_{j}^nd_{ij}\lambda_{ij}+\sum_{j=1}^n\int_0^{\sum_{i=1}^m\lambda_{ij}}w_j(x)dx+\sum_{i=1}^m\beta_i\left(\Lambda_i-\sum_{j=1}^n\lambda_{ij}\right)
+\label{Phi}\end{equation}
+
+To be able to obtain the PoA for a given instance the following mathematical program must be solved:
+
+$$\begin{array}{l@{\hspace{2cm}}l}\text{OPTMP:}&\text{NASHMP:}\\
+\text{minimise }(\ref{C})&\text{minimise }(\ref{Phi})
+\end{array}$$
+such that:
+\begin{equation}
+\sum_{j=1}^n\lambda_{ij}\leq\Lambda_{i}\text{ for all }i\in[m]\label{constraint 1}
+\end{equation}
+\begin{equation}
+\lambda_{ij}\in\mathbb{R}^{m\times n}_{\geq 0}\text{ for all }i\in[m],\;j\in[n]\label{constraint 2}
+\end{equation}
+\begin{equation}
+\sum_{i=1}^m\lambda_{ij}<c_j\mu_j\text{ for all }j\in[n]\label{constraint 3}
+\end{equation}
+
+The constant $\alpha_i\in\mathbb{R}_{\geq0}$ is simply a weighting statistic for the relative importance of travel distances to the other factors (once again allowing for this coefficient to be dependent on population partitioning).
+
+In \cite{} various theoretical results are proven.
 

### 2014-05-12 paper.tex
structure with stuff

@@
 In \cite{} various theoretical results are proven.
+With regards to the effect of worth of service on the PoA but also with regards to demand.
+The profile of Figure \ref{fig:poaprofile} is shown to hold in general.
+
+\begin{figure}[!hbtp]
+Pic
+\end{figure}
+
+To consider systems where individuals are able to observe the system there are two approaches: the first is to use a simulation based approach that allows individuals to choose their most desirable queue.
+One such approach that was considered specifically in the context of healthcare was considered in \cite{}.
+
+Given that individuals will consider a simple selfish decision rule this approach is relatively straightforward and can also be considered using straightforward analytical Markov models.
+The difficulty with this approach is appears when attempting to obtain the PoA.
+To carry this out an optimal policy must be obtained.
+
+In \cite{} various dynamic programming and approximate dynamic programming techniques are proposed that are able to not only give an optimal policy but also prove the following observation:
+
+\begin{center}
+\textit{Selfish users make busier systems.}
+\end{center}
+
+In the next section selfish congestion related decisions by managers will be considered.
 
@@
 
-\begin{itemize}
-    \item IK Paper
-\end{itemize}
+Talk about idea.
+Talk about Markov model.
+Talk about proof that pure strategy NE exists.
+Show how can be used to influence t.
 
@@
 
-\begin{itemize}
-    \item Describe model;
-    \item Show some results.
-\end{itemize}
+Describe simple Markov model for hospital.
+Describe routing game model for thing.
 

### 2014-05-12 Images/markovdiagram.tex
added a lot of stuff

\begin{tikzpicture}[scale=.7, every node/.style={scale=0.7}]
    % -----------------------------------------------
    % Boundaries ------------------------------------
    % -----------------------------------------------
    \draw [dashed, line width=1mm, red, opacity=.3] (12,2) -- (12,-20);
    \draw [dashed, line width=1mm, red, opacity=.3] (-2,-12) -- (20,-12);
    %\tikzstyle{state}=[ellipse, draw, fill=blue!10, minimum width=2cm];
    %\tikzstyle{state}=[rectangle, draw, fill=blue!10, minimum width=2cm];
    \tikzstyle{state}=[minimum width=2cm, font=\boldmath];
    %\draw  (0,0) rectangle (4,3);
    %\draw [dashed, red, thick] (0,1) -- (4,1);
    %\draw [dashed, red, thick] (3,0) -- (3,3);
    % -----------------------------------------------
    % First row--------------------------------------
    % -----------------------------------------------
    \node (aa) [state] at (0,0) {$(0,0)$};
    \node (ab) [state] at ($(aa) + (3,0)$) {$(0,1)$};
    \node (ac) [state] at ($(ab) + (3,0)$) {$(0,2)$};
    \node (ellipsisa1) at ($(ac) + (3,0)$) {$\dots$};
    \node(ak) [state] at ($(ellipsisa1) + (3,0)$) {$(0,K_{\RG})$};
    \node (ellipsisa2) at ($(ak) + (3,0)$) {$\dots$};
    \node(az) [state] at ($(ellipsisa2) + (3,0)$) {$(0,c_{\RG})$};
    % Transitions -----------------------------------
    % On Row:
    \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ab);
    \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ab);

    \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ac);
    \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ac);

    \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisa1);
    \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisa1);

    \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ak);
    \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ak);

    \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisa2);
    \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisa2);

    \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (az);
    \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (az);
    % -----------------------------------------------
    % Second row--------------------------------------
    % -----------------------------------------------
    \node (ba) [state] at (0,-3) {$(1,0)$};
    \node (bb) [state] at ($(ba) + (3,0)$) {$(1,1)$};
    \node (bc) [state] at ($(bb) + (3,0)$) {$(1,2)$};
    \node (ellipsisb1) at ($(bc) + (3,0)$) {$\dots$};
    \node(bk) [state] at ($(ellipsisb1) + (3,0)$) {$(1,K_{\RG})$};
    \node (ellipsisb2) at ($(bk) + (3,0)$) {$\dots$};
    \node(bz) [state] at ($(ellipsisb2) + (3,0)$) {$(1,c_{\RG})$};
    % Transitions -----------------------------------
    % On Row:
    \draw (ba) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bb);
    \draw (ba) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bb);

    \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bc);
    \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bc);

    \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisb1);
    \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisb1);

    \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bk);
    \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bk);

    \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisb2);
    \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisb2);

    \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (bz);
    \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bz);
    % With previous row:
    \draw (aa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ba);
    \draw (aa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ba);

    \draw (ab) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bb);
    \draw (ab) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bb);

    \draw (ac) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bc);
    \draw (ac) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bc);

    \draw (ellipsisa1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisb1);
    \draw (ellipsisa1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb1);

    \draw (ak) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bk);
    \draw (ak) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bk);

    \draw (ellipsisa2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisb2);
    \draw (ellipsisa2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb2);

    \draw (az) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bz);
    \draw (az) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bz);
    % -----------------------------------------------
    % Third row--------------------------------------
    % -----------------------------------------------
    \node (ca) [state] at (0,-6) {$(2,0)$};
    \node (cb) [state] at ($(ca) + (3,0)$) {$(2,1)$};
    \node (cc) [state] at ($(cb) + (3,0)$) {$(2,2)$};
    \node (ellipsisc1) at ($(cc) + (3,0)$) {$\dots$};
    \node(ck) [state] at ($(ellipsisc1) + (3,0)$) {$(2,K_{\RG})$};
    \node (ellipsisc2) at ($(ck) + (3,0)$) {$\dots$};
    \node(cz) [state] at ($(ellipsisc2) + (3,0)$) {$(2,c_{\RG})$};
    % Transitions -----------------------------------
    % On Row:
    \draw (ca) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cb);
    \draw (ca) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cb);

    \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cc);
    \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cc);

    \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisc1);
    \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisc1);

    \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ck);
    \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ck);

    \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisc2);
    \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisc2);

    \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (cz);
    \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cz);
    % With previous row:
    \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ca);
    \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ca);

    \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cb);
    \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cb);

    \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cc);
    \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cc);

    \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisc1);
    \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisc1);

    \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ck);
    \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ck);

    \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisc2);
    \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisc2);

    \draw (bz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (cz);
    \draw (bz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cz);
    % -----------------------------------------------
    % Fourth row--------------------------------------
    % -----------------------------------------------
    \node (da) at (0,-9) {$\vdots$};
    \node (db) at ($(da) + (3,0)$) {$\vdots$};
    \node (dc) at ($(db) + (3,0)$) {$\vdots$};
    \node (ellipsisd1) at ($(dc) + (3,0)$) {$\dots$};
    \node(dk) at ($(ellipsisd1) + (3,0)$) {$\vdots$};
    \node (ellipsisd2) at ($(dk) + (3,0)$) {$\dots$};
    \node(dz) at ($(ellipsisd2) + (3,0)$) {$\vdots$};
    % Transitions -----------------------------------
    % On Row:
    \draw (da) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (db);
    \draw (da) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (db);

    \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dc);
    \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dc);

    \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisd1);
    \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisd1);

    \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dk);
    \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dk);

    \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisd2);
    \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisd2);

    \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (dz);
    \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dz);
    % With previous row:
    \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (da);
    \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (da);

    \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (db);
    \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (db);

    \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (dc);
    \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dc);

    \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisd1);
    \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisd1);

    \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dk);
    \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dk);

    \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisd2);
    \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisd2);

    \draw (cz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dz);
    \draw (cz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dz);
    % -----------------------------------------------
    % Fifth row--------------------------------------
    % -----------------------------------------------
    \node (ea) [state] at (0,-12) {$(K_{\NH},0)$};
    \node (eb) [state] at ($(ea) + (3,0)$) {$(K_{\NH},1)$};
    \node (ec) [state] at ($(eb) + (3,0)$) {$(K_{\NH},2)$};
    \node (ellipsise1) at ($(ec) + (3,0)$) {$\dots$};
    \node(ek) [state] at ($(ellipsise1) + (3,0)$) {$(K_{\NH},K_{\RG})$};
    \node (ellipsise2) at ($(ek) + (3,0)$) {$\dots$};
    \node(ez) [state] at ($(ellipsise2) + (3,0)$) {$(K_{\NH},c_{\RG})$};
    % Transitions -----------------------------------
    % On Row:
    \draw (ea) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (eb);
    \draw (ea) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (eb);

    \draw (eb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ec);
    \draw (eb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ec);

    \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsise1);
    \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsise1);

    \draw (ellipsise1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ek);
    \draw (ellipsise1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ek);

    \draw (ek) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsise2);
    \draw (ek) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsise2);

    \draw (ellipsise2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ez);
    \draw (ellipsise2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ez);
    % With previous row:
    \draw (da) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ea);
    \draw (da) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ea);

    \draw (db) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (eb);
    \draw (db) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (eb);

    \draw (dc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ec);
    \draw (dc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ec);

    \draw (ellipsisd1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsise1);
    \draw (ellipsisd1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsise1);

    \draw (dk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ek);
    \draw (dk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ek);

    \draw (ellipsisd2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsise2);
    \draw (ellipsisd2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsise2);

    \draw (dz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ez);
    \draw (dz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ez);
    % Sixth row--------------------------------------
    \node (fa) at (0,-15) {$\vdots$};
    \node (fb) at ($(fa) + (3,0)$) {$\vdots$};
    \node (fc) at ($(fb) + (3,0)$) {$\vdots$};
    \node (ellipsisf1) at ($(fc) + (3,0)$) {$\dots$};
    \node(fk) at ($(ellipsisf1) + (3,0)$) {$\vdots$};
    \node (ellipsisf2) at ($(fk) + (3,0)$) {$\dots$};
    \node(fz) at ($(ellipsisf2) + (3,0)$) {$\vdots$};
    % Transitions -----------------------------------
    % On Row:
    \draw (fa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fb);
    \draw (fa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fb);

    \draw (fb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fc);
    \draw (fb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fc);

    \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsisf1);
    \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisf1);

    \draw (ellipsisf1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fk);
    \draw (ellipsisf1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fk);

    \draw (fk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisf2);
    \draw (fk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisf2);

    \draw (ellipsisf2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (fz);
    \draw (ellipsisf2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fz);
    % With previous row:
    \draw (ea) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fa);
    \draw (ea) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fa);

    \draw (eb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fb);
    \draw (eb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fb);

    \draw (ec) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fc);
    \draw (ec) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fc);

    \draw (ellipsise1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisf1);
    \draw (ellipsise1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisf1);

    \draw (ek) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (fk);
    \draw (ek) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fk);

    \draw (ellipsise2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisf2);
    \draw (ellipsise2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisf2);

    \draw (ez) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (fz);
    \draw (ez) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fz);
    % Final row--------------------------------------
    \node (za) [state] at (0,-18) {$(c_{\NH},0)$};
    \node (zb) [state] at ($(za) + (3,0)$) {$(c_{\NH},1)$};
    \node (zc) [state] at ($(zb) + (3,0)$) {$(c_{\NH},2)$};
    \node (ellipsisz1) at ($(zc) + (3,0)$) {$\dots$};
    \node(zk) [state] at ($(ellipsisz1) + (3,0)$) {$(c_{\NH},K_{\RG})$};
    \node (ellipsisz2) at ($(zk) + (3,0)$) {$\dots$};
    \node(zz) [state] at ($(ellipsisz2) + (3,0)$) {$(c_{\NH},c_{\RG})$};
    % Transitions -----------------------------------
    % On Row:
    \draw (za) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zb);
    \draw (za) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zb);

    \draw (zb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zc);
    \draw (zb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zc);

    \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz1);
    \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisz1);

    \draw (ellipsisz1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zk);
    \draw (ellipsisz1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zk);

    \draw (zk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz2);
    \draw (zk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisz2);

    \draw (ellipsisz2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zz);
    \draw (ellipsisz2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zz);
    % With previous row:
    \draw (fa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (za);
    \draw (fa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (za);

    \draw (fb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zb);
    \draw (fb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zb);

    \draw (fc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zc);
    \draw (fc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zc);

    \draw (ellipsisf1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisz1);
    \draw (ellipsisf1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisz1);

    \draw (fk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zk);
    \draw (fk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zk);

    \draw (ellipsisf2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisz2);
    \draw (ellipsisf2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisz2);

    \draw (fz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zz);
    \draw (fz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zz);

\end{tikzpicture}

### 2014-05-12 paper.tex
added a lot of stuff

@@
 \usepackage{tikz}
-\usepackage{parskip}
+\usetikzlibrary{calc}
+\usetikzlibrary{shapes}
+\usetikzlibrary{arrows}
+\usetikzlibrary{backgrounds}
+
+\usepackage[parfill]{parskip}
+
+\newcommand{\NH}{\text{NH}}
+\newcommand{\RG}{\text{RG}}
 
@@
 
-Talk about idea.
-Talk about Markov model.
-Talk about proof that pure strategy NE exists.
-Show how can be used to influence t.
+The main proposition of the work requested by the ABUHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
+After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
+As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
+This state dependent model was applied to both NH and RG separately.
+It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
+A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.
+
+\begin{figure}[!htbp]
+\begin{center}
+\begin{tikzpicture}
+\node (A) at (0,0) [draw] {RG};
+\node (B) at (2,0) [draw] {NH};
+\draw [->] (-1,0) -- (A);
+\draw [->] (3,0) -- (B);
+\draw [->] (-1,0) -- ($(A)+(-.5,0)$) -- ($(A)+(-.5,.5)$) -- ($(A)+(.5,.5)$) -- ($(A)+(.5,.1)$) -- ($(B)+(-.4,.1)$);
+\draw [->] (3,0) -- ($(B)+(.5,0)$) -- ($(B)+(.5,-.5)$) -- ($(B)+(-.5,-.5)$) -- ($(B)+(-.5,-.1)$) -- ($(A)+(.4,-.1)$);
+\draw [->] (3,0) -- (B);
+\node at ($(A) + (0,.8)$) {Divert?};
+\node at ($(B) + (0,-.8)$) {Divert?};
+\end{tikzpicture}
+\caption{Diagrammatic representation of CCU interaction through patient diversion.}\label{diagramofdiversion}
+\end{center}
+\end{figure}
+
+The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{\NH,\RG\}$. Note that $0\leq K_h\leq c_h$.
+
+\begin{figure}[!htbp]
+\begin{center}
+    \begin{tikzpicture}
+        \draw  (0,0) rectangle (4,3);
+        \draw [dashed, red, thick] (0,1) -- (4,1);
+        \draw [dashed, red, thick] (3,0) -- (3,3);
+        \node at (-.5,1) {$K_{\NH}$};
+        \node at (3,3.25) {$K_{\RG}$};
+        \node at (1.5,2) {$\lambda_{h}^{(a)}$};
+        \node at (3.5,2) {$\lambda_{h}^{(b)}$};
+        \node at (1.5,.5) {$\lambda_{h}^{(c)}$};
+        \node at (3.5,.5) {$\lambda_{h}^{(d)}$};
+    \end{tikzpicture}
+\caption{General arrival rates for each CCU at each region, where $h\in\{\NH, \RG\}$} \label{arrivalrateregions}
+\end{center}
+\end{figure}
+
+\begin{figure}[!htbp]
+\begin{center}
+\input{Images/markovdiagram.tex}
+\caption{Generic Markov chain underpinning the queueing model of this paper} \label{mc}
+\end{center}
+\end{figure}
+
+Utilities will be of interest when this queueing theoretical model will be inserted in the game theoretical model.
+Throughput of patients is a natural choice of utility given that most hospitals are financially rewarded per served patient \cite{Pate2009}.
+For each threshold pair $(K_{\NH},K_{\RG})$, the utilisation rate $U_h$ and throughput $T_h$ can easily be obtained for each CCU: $h\in\{\text{NH},\text{RG}\}$, using the following formulas:
+
+$$U_{h}={{\sum_{n=0}^{c_h} nP^{(h)}(n)}\over{c_{h}}}$$
+$$T_{h}=\mu_h \sum _{n=0}^{c_h} nP^{(h)}(n)$$
+
+where $P^{(h)}=P^{(h)}(K_{\NH},K_{\RG})$ is the steady state probability distribution function (obtained from the corresponding transition matrix $Q=Q(K_{\NH},K_{\RG})$) for $h\in\{\text{NH},\text{RG}\}$.
+
+For $c_{\NH}=8$, $c_{\RG}=16$, $\lambda_{\NH}=(\lambda_{\NH}^{(a)},\lambda_{\NH}^{(b)},\lambda_{\NH}^{(c)},\lambda_{\NH}^{(d)})=(1.5,3.74,0,0)$, $\lambda_{\RG}=(\lambda_{\RG}^{(a)},\lambda_{\RG}^{(b)},\lambda_{\RG}^{(c)},\lambda_{\RG}^{(d)})=(2.24,0,3.74,0)$ and $(K_{\NH},K_{\RG})=(6,12)$, the steady state probabilities for each CCU are given in Figure \ref{steady_state_probs}.
+
+\begin{figure}[!htbp]
+\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
+$$\left(U_{h}-t\right)^2$$
+\hspace{2cm}Subject to:
+\begin{align}
+0\leq & K_h \leq c_{h}\nonumber\\
+&K_h \in  \mathbb{Z}\nonumber
+\end{align}
+\caption{The optimisation problem underlying the game}\label{model1}
+\end{figure}
+
+This game is equivalent to a bi matrix game with restriction to pure strategies where both players aim to get their utilisation as close as possible to a certain target.
+As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABUHB, long term threshold policies are a realistic consideration.
+
+The following result is a sufficient condition for the existence of an equilibrium:\\
+
+\textbf{Theorem.}
+
+Let $f_{h}(k):[1,c_{\bar h}]\to[1,c_h]$ be the best response of player $h\in\{\NH, \RG\}$ to the diversion threshold of $\bar h\ne h$ ($\bar h\in\{\NH, \RG\}$).
+
+If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of Figure \ref{model1} has at least one Nash Equilibrium.
+
+\textbf{proof}
+
+The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set (in case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value).
+
+As such if $f_h$ is non-decreasing then it is in fact a stepwise non-decreasing function.
+If we consider $f_{\NH}$ and $f_{\RG}$ plotted on the same axis (so that the domain of $f_{\NH}$ is the $x$-axis and the domain of $f_{\RG}$ is the y-axis) it is obvious to see that the functions must intersect at some point as shown in Figure \ref{exampleforproof}.
+
+\begin{figure}[!htbp]
+$$\begin{array}{cc}
+\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_NH.pdf}&
+\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_RG.pdf}
+\end{array}$$
+\caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
+\end{figure}
+
+This point of intersection corresponds to a Nash Equilibrium of Figure \ref{model1}.
+$\square$
+
+\begin{figure}[!htbp]
+\begin{center}
+\includegraphics[width=12cm]{./Images/argminPoAmodel2.pdf}
+\caption{Lowest value of $t$ ensuring PoA$=1$} \label{mintargetvdemandmodel2}
+\end{center}
+\end{figure}
 

### 2014-05-13 paper.tex
Have a bunch of stuff added

@@
 \begin{abstract}
-Describe paper.
+It is well observed that individual behaviour can have an effect on the efficiency of queueing systems.
+The impact of this behaviour on the economic efficiency of public services is considered in this paper where we present results concerning the congestion related implications of decisions made by individuals when choosing between facilities.
+The work presented has important managerial implications at a public policy level when considering the effect of allowing individuals to choose between providers.
+We show that in general the introduction of choice in an already inefficient system will not have a negative effect.
+Introducing choice in a system that copes with demand will have a negative effect.
 \end{abstract}
@@
 
-\begin{itemize}
-    \item Review GT in HC in general (small);
-    \item Review congestion type games;
-    \item PoA;
-    \item Structure.
-\end{itemize}
+What damage do the selfish choices of some afflict on to the welfare of all? The work presented in this paper answers this question in the context of public service systems.
+
+There is a substantial quantity of literature on the subject of equilibrium behaviour of a queueing system where congestion is a factor influencing behaviour \cite{Adler1969,Bell1983,Edelson1971,Knudsen1972,Luski1976,Naor1969,Yechiali1972}.
+This can be traced back to a series of short communications between Leeman \cite{Leeman1964,Leeman1965} and Saaty \cite{Saaty1965}.
+This paper builds on this literature by considering the problem of public service systems.
+For most public services, congestion is a negative aspect of service quality.
+Examples of this are healthcare systems (waiting lists), transports systems (traffic jams) and/or schools (overcrowding of class rooms).
+
+The degree of central control that should be exercised is a very important question to be considered by governments and/or policy makers.
+What is the effect of allowing individuals to choose service provider?
+
+Of course, the motivation for the introduction of choice is to create competition in the hope that this would improve overall service quality.
+The aim of the work presented here is to use a game theoretical approach to measure the immediate effect of choice (i.e.
+prior to the effect of competition).
+The approach proposed is based on a measure called \emph{the price of anarchy} \cite{Chau2003,Cole2006,Correa2008,Gilboa-Freedman2009,Haviv2007,Musacchio2009,Roughgarden2003,Roughgarden2005,Roughgarden2004,Skinner2010}.
+First introduced in \cite{Koutsoupias1999} (a conference paper that has been reprinted in \cite{Koutsoupias2009}), the price of anarchy is the ratio of the costs of the worst possible Nash equilibrium and the social optimum, and can therefore be interpreted as a measure of the efficiency of a system.
+
+Game theory is the mathematical study of interactive decision making between rational decision makers \cite{Maschler2013}.
+A game is a description of strategic interactions that includes the constraints on the actions that the players can take and on the players' interests.
+
+Most research where game theory is applied in healthcare has mainly concentrated on Emergency Departments (EDs) and how to deal with diversions of patients and ambulances.
+In \cite{Hagtvedt2009} cooperative strategies for hospitals are considered, in order to reduce occurrences when ambulances are turned away due to the ED being full.
+In \cite{Deo2011} a queueing network model of two EDs is proposed to study the network effect of ambulance diversion.
+Each ED aims to minimise the expected waiting time of its patients (walk-ins and ambulances) and chooses its diversion threshold based on the number of patients at its location.
+Decentralised decision making in the network is modelled as a non-cooperative game.
+
+Some other work that has not concentrated on EDs, but has been applied to healthcare includes: \cite{Knight2013}, where results concerning the congestion related implications of decisions made by patients when choosing between healthcare facilities were presented.
+In \cite{Howard2002} a model of the accept/reject decision for transplant organs is developed.
+
+In the wider intersection of game theory and queueing theory (where this work lies) papers that consider price and/or capacity include: \cite{Allon2007, Cachon2002,  Cachon2007, Kalai1992, Levhari1978}.
+In these models, the choice of price/or capacity determines the arrival rate for each firm; this is similar to the approach taken in this paper.
 
@@
 \begin{figure}[!hbtp]
-Show diagram.
+\begin{center}
+\includegraphics[width=.7\textwidth]{./Images/Hospital_Choices.pdf}
+\end{center}
+\caption{Routing patients from $m$ hospitals to $n$ services.}\label{fig:choices}
 \end{figure}
@@
 \begin{figure}[!hbtp]
-Show routing game image.
+\begin{center}
+\includegraphics[width=.7\textwidth]{./Images/Hospital_Routing_Game.pdf}
+\end{center}
+\caption{Routing game $m$ hospitals to $n$ services.}\label{fig:routinggame}
 \end{figure}
@@
 \begin{figure}[!hbtp]
-Pic
+\begin{center}
+\includegraphics[width=.7\textwidth]{./Images/PoAPlotForSimpleDiagram.pdf}
+\end{center}
+\caption{General profile of PoA.}\label{fig:poaprofile}
 \end{figure}
@@
 
-\section{EU and EMV Interface}
-
-Describe simple Markov model for hospital.
-Describe routing game model for thing.
-
 \section{Conclusions}
 
-\bigskip
-\noindent{\bf Refer\^encias}
+\begin{itemize}
+    \item Describe potential
+    \item Describe further work
+    \item Discuss potential for heuristic approaches
+\end{itemize}
 
-\noindent \textbf {Anna, A.} (1996), Comunica\c c\~ao, \textit{Atas do XXVIII SBPO}, 123-134.
+\newpage
+\bibliographystyle{plain}
+\bibliography{library.bib}
 
-\noindent \textbf{Gates, B.}, \textit{Um Livro Muito Bom}, Editor, Local, 2003.
-
-\noindent  \textbf{Pel\'e, E. N. e Rom\'ario, R. R.}, Exemplo de artigo em livro, em Windows, P. T. e Linux, V. G. (Eds.),
-\textit{Colet\^ania de Artigos},  Editor, Local, 123-133, 2004.
-
-\noindent  \textbf{Silva, A. B., Souza, C. D. e Santos, E. F.}, T\'\i tulo de um relat\'orio t\'ecnico dispon\'\i vel na Internet,
-\textit{ Relat\'orios de Pesquisa em Engenharia de Produ\c c\~ao}, n. 4,  Universidade Z,
-1999
-
-\noindent{(www.universidade.br/rel, 4, 2001.}
-
-\noindent  \textbf{Smith, S. e Jones, J.} (2002), A paper on Operations Research, \textit{Pesquisa Operacional},
-32, 5-44.
+%\bigskip
+%\noindent{\bf Refer\^encias}
+%
+%\noindent \textbf {Anna, A.} (1996), Comunica\c c\~ao, \textit{Atas do XXVIII SBPO}, 123-134.
+%
+%\noindent \textbf{Gates, B.}, \textit{Um Livro Muito Bom}, Editor, Local, 2003.
+%
+%\noindent  \textbf{Pel\'e, E. N. e Rom\'ario, R. R.}, Exemplo de artigo em livro, em Windows, P. T. e Linux, V. G. (Eds.),
+%\textit{Colet\^ania de Artigos},  Editor, Local, 123-133, 2004.
+%
+%\noindent  \textbf{Silva, A. B., Souza, C. D. e Santos, E. F.}, T\'\i tulo de um relat\'orio t\'ecnico dispon\'\i vel na Internet,
+%\textit{ Relat\'orios de Pesquisa em Engenharia de Produ\c c\~ao}, n. 4,  Universidade Z,
+%1999
+%
+%\noindent{(www.universidade.br/rel, 4, 2001.}
+%
+%\noindent  \textbf{Smith, S. e Jones, J.} (2002), A paper on Operations Research, \textit{Pesquisa Operacional},
+%32, 5-44.
 

### 2014-05-13 paper.tex
abstract written

@@
 \begin{abstract}
-It is well observed that individual behaviour can have an effect on the efficiency of queueing systems.
-The impact of this behaviour on the economic efficiency of public services is considered in this paper where we present results concerning the congestion related implications of decisions made by individuals when choosing between facilities.
-The work presented has important managerial implications at a public policy level when considering the effect of allowing individuals to choose between providers.
-We show that in general the introduction of choice in an already inefficient system will not have a negative effect.
-Introducing choice in a system that copes with demand will have a negative effect.
+Individual behaviour has an effect on the optimal control of queueing systems.
+This idea sits at the intersection of queueing theory and game theory.
+The role of this paper is to discuss some work in this area applied to healthcare systems.
+
+One aspect considered is the effect of patient behaviour when choosing between service facilities.
+Various pieces of work will be discussed that have looked at this area.
+
+A second aspect is the effect that managers may have when acting rationally in their control of queueing systems.
 \end{abstract}

### 2014-05-13 paper.tex
Finished intro

@@
 
-What damage do the selfish choices of some afflict on to the welfare of all? The work presented in this paper answers this question in the context of public service systems.
+Understanding the effect of selfish individuals in queueing systems can be traced back to a series of short communications between Leeman \cite{Leeman1964,Leeman1965} and Saaty \cite{Saaty1965}.
 
-There is a substantial quantity of literature on the subject of equilibrium behaviour of a queueing system where congestion is a factor influencing behaviour \cite{Adler1969,Bell1983,Edelson1971,Knudsen1972,Luski1976,Naor1969,Yechiali1972}.
-This can be traced back to a series of short communications between Leeman \cite{Leeman1964,Leeman1965} and Saaty \cite{Saaty1965}.
-This paper builds on this literature by considering the problem of public service systems.
-For most public services, congestion is a negative aspect of service quality.
-Examples of this are healthcare systems (waiting lists), transports systems (traffic jams) and/or schools (overcrowding of class rooms).
-
-The degree of central control that should be exercised is a very important question to be considered by governments and/or policy makers.
-What is the effect of allowing individuals to choose service provider?
-
-Of course, the motivation for the introduction of choice is to create competition in the hope that this would improve overall service quality.
-The aim of the work presented here is to use a game theoretical approach to measure the immediate effect of choice (i.e.
-prior to the effect of competition).
-The approach proposed is based on a measure called \emph{the price of anarchy} \cite{Chau2003,Cole2006,Correa2008,Gilboa-Freedman2009,Haviv2007,Musacchio2009,Roughgarden2003,Roughgarden2005,Roughgarden2004,Skinner2010}.
-First introduced in \cite{Koutsoupias1999} (a conference paper that has been reprinted in \cite{Koutsoupias2009}), the price of anarchy is the ratio of the costs of the worst possible Nash equilibrium and the social optimum, and can therefore be interpreted as a measure of the efficiency of a system.
-
-Game theory is the mathematical study of interactive decision making between rational decision makers \cite{Maschler2013}.
-A game is a description of strategic interactions that includes the constraints on the actions that the players can take and on the players' interests.
+In \cite{Adler1969,Bell1983,Edelson1971,Knudsen1972,Luski1976,Naor1969,Yechiali1972} a variety of models are discussed that obtain optimal and equilibrium behaviour in situations where individuals can choose between a best queue to join.
+Most of the work considers these systems in a theoretical context.
 
@@
 
-Some other work that has not concentrated on EDs, but has been applied to healthcare includes: \cite{Knight2013}, where results concerning the congestion related implications of decisions made by patients when choosing between healthcare facilities were presented.
-In \cite{Howard2002} a model of the accept/reject decision for transplant organs is developed.
+The degree of central control that should be exercised is a very important question to be considered by governments and/or policy makers.
+What is the effect of allowing individuals to choose service provider?
 
-In the wider intersection of game theory and queueing theory (where this work lies) papers that consider price and/or capacity include: \cite{Allon2007, Cachon2002,  Cachon2007, Kalai1992, Levhari1978}.
-In these models, the choice of price/or capacity determines the arrival rate for each firm; this is similar to the approach taken in this paper.
+This is a question that is answered using the Game theoretical concept referred to as the \textit{Price of Anarchy} (PoA).
+The PoA is defined as the ratio of the selfish utility to the optimal utility.
 
-\section{Choosing queues}
+Section \label{sec:choosingqueues} will discuss some PoA analysis applied to individuals choosing between queues.
+Section \label{sec:managingqueues} will discuss similar analysis in the case of selfish behaviour related to the management of queues.
+Section \label{sec:conclusion} will conclude with a summary and thoughts for further work.
+
+\section{Choosing queues}\label{sec:choosingqueues}
 
@@
 
-\section{CCU Work}
+\section{Managing queues}\label{sec:managingqueues}
 
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:conclusion}
 

### 2014-05-13 paper.tex
Introduction written

@@
 \usepackage{amsmath,amssymb}
+\usepackage{booktabs}
 
 \usepackage{tikz}
+
 \usetikzlibrary{calc}
@@
 This is a question that is answered using the Game theoretical concept referred to as the \textit{Price of Anarchy} (PoA).
+This was first defined in \cite{Koutsoupias2009} but an excellent introduction is given in \cite{Roughgarden2005}.
 The PoA is defined as the ratio of the selfish utility to the optimal utility.
@@
 In particular the situation shown diagrammatically in Figure \ref{fig:choices} is considered: patients have a choice amongst $M/M/c$ queues.
+Each $M/M/c$ queue corresponds to a (simple) model of a Hospital (or indeed any other public service facility).
 
@@
 
+The parameters of this system are shown in Table \ref{tab:parameters}.
+
+\begin{figure}[!hbtp]
+\begin{center}
+\begin{tabular}{cl}
+\toprule
+Parameter & Interpretation\\
+\midrule
+$m\in\mathbb{Z}$& Number of sources\\
+$n\in\mathbb{Z}$& Number of service centers\\
+$\beta\in\mathbb{R}_{\geq 0}^{m}$& Worth of service\\
+$\Lambda\in\mathbb{R}_{\geq 0}^{m}$& Demand rate\\
+$w_j$ for $j\in[n]$& A convex utility function\\
+$d_{ij}$ for $i\in[m],\;j\in[n]$& Distance from source $i$ to service center $j$\\
+$\lambda_{ij}$ for $i\in[m],\;j\in[n]$& Traffic from source $i$ to service center $j$\\
+\toprule
+\end{tabular}
+\caption{Parameters of model}\label{tab:parameters}
+\end{center}
+\end{figure}
+
 There are two approaches to solving this problem: assuming that patients observe or not the system states before choosing a facility.
-A rigorous comparison of these two approaches for individuals choosing to join an $M/M/1$ queue is given in \cite{}.
+A rigorous comparison of these two approaches for individuals choosing to join an $M/M/1$ queue is given in \cite{shone2013comparisons}.
 
-An unobservable study is given in \cite{} where routing games \cite{Rouhgharden} are used to study the system described.
+An unobservable study is given in \cite{Knight2013} where routing games \cite{Roughgarden2005} are used to study the system described.
 The routing game used is shown in \ref{fig:routinggame}.
@@
 
-It can be shown that the cost for any given flow $\lambda$ (denoting the amount of traffic from source $i$ to facility $j$) corresponds to...
+The corresponding cost function for a given traffic flow $\lambda$ is given by:
 
@@
 
-Obtaining the Nash flow: ie the equilibrium behaviour.
+The constant $\alpha_i\in\mathbb{R}_{\geq0}$ is simply a weighting statistic for the relative importance of travel distances to the other factors (once again allowing for this coefficient to be dependent on population partitioning).
+The Nash flow corresponding to the flow at which all traffic from a given source travels on minimal paths can be shown to be given by the flow that minimises the following function:
 
@@
 
-The constant $\alpha_i\in\mathbb{R}_{\geq0}$ is simply a weighting statistic for the relative importance of travel distances to the other factors (once again allowing for this coefficient to be dependent on population partitioning).
-
-In \cite{} various theoretical results are proven.
-With regards to the effect of worth of service on the PoA but also with regards to demand.
+In \cite{Knight2013} various theoretical results are proven with regards to the effect of worth of service on the PoA but also with regards to demand.
 The profile of Figure \ref{fig:poaprofile} is shown to hold in general.
@@
 
+Further to the theoretical consideration the PoA was calculated for a large case study using Hospital in Wales offering knee surgeries.
+A high PoA was calculated for the current demand.
+
 To consider systems where individuals are able to observe the system there are two approaches: the first is to use a simulation based approach that allows individuals to choose their most desirable queue.
-One such approach that was considered specifically in the context of healthcare was considered in \cite{}.
+One such approach that was considered specifically in the context of healthcare was considered in \cite{Knight2010}.
 
@@
 The difficulty with this approach is appears when attempting to obtain the PoA.
-To carry this out an optimal policy must be obtained.
 
-In \cite{} various dynamic programming and approximate dynamic programming techniques are proposed that are able to not only give an optimal policy but also prove the following observation:
+In \cite{Shone2014} various dynamic programming and approximate dynamic programming techniques are proposed that are able to not only give an optimal policy but also prove the following observation:
 
@@
 \bibliographystyle{plain}
-\bibliography{library.bib}
+\bibliography{library}
 

### 2014-05-13 paper.tex
backslash has dissapeared

@@
 
+Following the analysis of two critical care units (CCUs) it was found that the only a state dependent queueing model (where the demand rate to each CCU depended on the state of the CCU) would give a valid representation of the system.
+Upon discussion with the managers in question, it was acknowledged that certain behaviours took place.
+Indeed when one CCU was at high capacity it was likely to divert patients to the other CCU.
+
+In ...
 The main proposition of the work requested by the ABUHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.

### 2014-05-13 Images/markovdiagram.tex
Section 2 done

@@
     \node (ellipsisa1) at ($(ac) + (3,0)$) {$\dots$};
-    \node(ak) [state] at ($(ellipsisa1) + (3,0)$) {$(0,K_{\RG})$};
+    \node(ak) [state] at ($(ellipsisa1) + (3,0)$) {$(0,K_{1})$};
     \node (ellipsisa2) at ($(ak) + (3,0)$) {$\dots$};
-    \node(az) [state] at ($(ellipsisa2) + (3,0)$) {$(0,c_{\RG})$};
+    \node(az) [state] at ($(ellipsisa2) + (3,0)$) {$(0,c_{1})$};
     % Transitions -----------------------------------
     % On Row:
-    \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ab);
-    \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ab);
+    \draw (aa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (ab);
+    \draw (aa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ab);
 
-    \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ac);
-    \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ac);
+    \draw (ab) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (ac);
+    \draw (ab) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ac);
 
-    \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisa1);
-    \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisa1);
+    \draw (ac) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (ellipsisa1);
+    \draw (ac) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisa1);
 
-    \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ak);
-    \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ak);
+    \draw (ellipsisa1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (ak);
+    \draw (ellipsisa1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ak);
 
-    \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisa2);
-    \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisa2);
+    \draw (ak) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(b)}$} (ellipsisa2);
+    \draw (ak) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisa2);
 
-    \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (az);
-    \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (az);
+    \draw (ellipsisa2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(b)}$} (az);
+    \draw (ellipsisa2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (az);
     % -----------------------------------------------
@@
     \node (ellipsisb1) at ($(bc) + (3,0)$) {$\dots$};
-    \node(bk) [state] at ($(ellipsisb1) + (3,0)$) {$(1,K_{\RG})$};
+    \node(bk) [state] at ($(ellipsisb1) + (3,0)$) {$(1,K_{1})$};
     \node (ellipsisb2) at ($(bk) + (3,0)$) {$\dots$};
-    \node(bz) [state] at ($(ellipsisb2) + (3,0)$) {$(1,c_{\RG})$};
+    \node(bz) [state] at ($(ellipsisb2) + (3,0)$) {$(1,c_{1})$};
     % Transitions -----------------------------------
     % On Row:
-    \draw (ba) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bb);
-    \draw (ba) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bb);
+    \draw (ba) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (bb);
+    \draw (ba) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (bb);
 
-    \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bc);
-    \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bc);
+    \draw (bb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (bc);
+    \draw (bb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (bc);
 
-    \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisb1);
-    \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisb1);
+    \draw (bc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (ellipsisb1);
+    \draw (bc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisb1);
 
-    \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (bk);
-    \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bk);
+    \draw (ellipsisb1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (bk);
+    \draw (ellipsisb1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (bk);
 
-    \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisb2);
-    \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisb2);
+    \draw (bk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(b)}$} (ellipsisb2);
+    \draw (bk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisb2);
 
-    \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (bz);
-    \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (bz);
+    \draw (ellipsisb2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(b)}$} (bz);
+    \draw (ellipsisb2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (bz);
     % With previous row:
-    \draw (aa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ba);
-    \draw (aa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ba);
+    \draw (aa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (ba);
+    \draw (aa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ba);
 
-    \draw (ab) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bb);
-    \draw (ab) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bb);
+    \draw (ab) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (bb);
+    \draw (ab) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (bb);
 
-    \draw (ac) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (bc);
-    \draw (ac) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bc);
+    \draw (ac) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (bc);
+    \draw (ac) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (bc);
 
-    \draw (ellipsisa1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisb1);
-    \draw (ellipsisa1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb1);
+    \draw (ellipsisa1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (ellipsisb1);
+    \draw (ellipsisa1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisb1);
 
-    \draw (ak) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bk);
-    \draw (ak) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bk);
+    \draw (ak) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (bk);
+    \draw (ak) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (bk);
 
-    \draw (ellipsisa2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisb2);
-    \draw (ellipsisa2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisb2);
+    \draw (ellipsisa2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (ellipsisb2);
+    \draw (ellipsisa2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisb2);
 
-    \draw (az) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (bz);
-    \draw (az) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (bz);
+    \draw (az) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (bz);
+    \draw (az) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (bz);
     % -----------------------------------------------
@@
     \node (ellipsisc1) at ($(cc) + (3,0)$) {$\dots$};
-    \node(ck) [state] at ($(ellipsisc1) + (3,0)$) {$(2,K_{\RG})$};
+    \node(ck) [state] at ($(ellipsisc1) + (3,0)$) {$(2,K_{1})$};
     \node (ellipsisc2) at ($(ck) + (3,0)$) {$\dots$};
-    \node(cz) [state] at ($(ellipsisc2) + (3,0)$) {$(2,c_{\RG})$};
+    \node(cz) [state] at ($(ellipsisc2) + (3,0)$) {$(2,c_{1})$};
     % Transitions -----------------------------------
     % On Row:
-    \draw (ca) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cb);
-    \draw (ca) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cb);
+    \draw (ca) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (cb);
+    \draw (ca) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (cb);
 
-    \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (cc);
-    \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cc);
+    \draw (cb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (cc);
+    \draw (cb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (cc);
 
-    \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisc1);
-    \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisc1);
+    \draw (cc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (ellipsisc1);
+    \draw (cc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisc1);
 
-    \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ck);
-    \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ck);
+    \draw (ellipsisc1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (ck);
+    \draw (ellipsisc1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ck);
 
-    \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisc2);
-    \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisc2);
+    \draw (ck) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(b)}$} (ellipsisc2);
+    \draw (ck) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisc2);
 
-    \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (cz);
-    \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (cz);
+    \draw (ellipsisc2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(b)}$} (cz);
+    \draw (ellipsisc2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (cz);
     % With previous row:
-    \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ca);
-    \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ca);
+    \draw (ba) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (ca);
+    \draw (ba) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ca);
 
-    \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cb);
-    \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cb);
+    \draw (bb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (cb);
+    \draw (bb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (cb);
 
-    \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (cc);
-    \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cc);
+    \draw (bc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (cc);
+    \draw (bc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (cc);
 
-    \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisc1);
-    \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisc1);
+    \draw (ellipsisb1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (ellipsisc1);
+    \draw (ellipsisb1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisc1);
 
-    \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ck);
-    \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ck);
+    \draw (bk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (ck);
+    \draw (bk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ck);
 
-    \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisc2);
-    \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisc2);
+    \draw (ellipsisb2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (ellipsisc2);
+    \draw (ellipsisb2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisc2);
 
-    \draw (bz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (cz);
-    \draw (bz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (cz);
+    \draw (bz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (cz);
+    \draw (bz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (cz);
     % -----------------------------------------------
@@
     % On Row:
-    \draw (da) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (db);
-    \draw (da) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (db);
+    \draw (da) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (db);
+    \draw (da) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (db);
 
-    \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dc);
-    \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dc);
+    \draw (db) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (dc);
+    \draw (db) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (dc);
 
-    \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (ellipsisd1);
-    \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisd1);
+    \draw (dc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (ellipsisd1);
+    \draw (dc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisd1);
 
-    \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(a)}$} (dk);
-    \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dk);
+    \draw (ellipsisd1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(a)}$} (dk);
+    \draw (ellipsisd1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (dk);
 
-    \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (ellipsisd2);
-    \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisd2);
+    \draw (dk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(b)}$} (ellipsisd2);
+    \draw (dk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisd2);
 
-    \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(b)}$} (dz);
-    \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (dz);
+    \draw (ellipsisd2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(b)}$} (dz);
+    \draw (ellipsisd2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (dz);
     % With previous row:
-    \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (da);
-    \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (da);
+    \draw (ca) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (da);
+    \draw (ca) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (da);
 
-    \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (db);
-    \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (db);
+    \draw (cb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (db);
+    \draw (cb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (db);
 
-    \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (dc);
-    \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dc);
+    \draw (cc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (dc);
+    \draw (cc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (dc);
 
-    \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsisd1);
-    \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisd1);
+    \draw (ellipsisc1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (ellipsisd1);
+    \draw (ellipsisc1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisd1);
 
-    \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dk);
-    \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dk);
+    \draw (ck) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (dk);
+    \draw (ck) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (dk);
 
-    \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsisd2);
-    \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisd2);
+    \draw (ellipsisc2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (ellipsisd2);
+    \draw (ellipsisc2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisd2);
 
-    \draw (cz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (dz);
-    \draw (cz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (dz);
+    \draw (cz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (dz);
+    \draw (cz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (dz);
     % -----------------------------------------------
@@
     % -----------------------------------------------
-    \node (ea) [state] at (0,-12) {$(K_{\NH},0)$};
-    \node (eb) [state] at ($(ea) + (3,0)$) {$(K_{\NH},1)$};
-    \node (ec) [state] at ($(eb) + (3,0)$) {$(K_{\NH},2)$};
+    \node (ea) [state] at (0,-12) {$(K_{2},0)$};
+    \node (eb) [state] at ($(ea) + (3,0)$) {$(K_{2},1)$};
+    \node (ec) [state] at ($(eb) + (3,0)$) {$(K_{2},2)$};
     \node (ellipsise1) at ($(ec) + (3,0)$) {$\dots$};
-    \node(ek) [state] at ($(ellipsise1) + (3,0)$) {$(K_{\NH},K_{\RG})$};
+    \node(ek) [state] at ($(ellipsise1) + (3,0)$) {$(K_{2},K_{1})$};
     \node (ellipsise2) at ($(ek) + (3,0)$) {$\dots$};
-    \node(ez) [state] at ($(ellipsise2) + (3,0)$) {$(K_{\NH},c_{\RG})$};
+    \node(ez) [state] at ($(ellipsise2) + (3,0)$) {$(K_{2},c_{1})$};
     % Transitions -----------------------------------
     % On Row:
-    \draw (ea) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (eb);
-    \draw (ea) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (eb);
+    \draw (ea) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(c)}$} (eb);
+    \draw (ea) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (eb);
 
-    \draw (eb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ec);
-    \draw (eb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ec);
+    \draw (eb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(c)}$} (ec);
+    \draw (eb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ec);
 
-    \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsise1);
-    \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsise1);
+    \draw (ec) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(c)}$} (ellipsise1);
+    \draw (ec) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsise1);
 
-    \draw (ellipsise1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ek);
-    \draw (ellipsise1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ek);
+    \draw (ellipsise1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(c)}$} (ek);
+    \draw (ellipsise1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ek);
 
-    \draw (ek) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsise2);
-    \draw (ek) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsise2);
+    \draw (ek) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (ellipsise2);
+    \draw (ek) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsise2);
 
-    \draw (ellipsise2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ez);
-    \draw (ellipsise2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ez);
+    \draw (ellipsise2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (ez);
+    \draw (ellipsise2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ez);
     % With previous row:
-    \draw (da) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ea);
-    \draw (da) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ea);
+    \draw (da) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (ea);
+    \draw (da) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ea);
 
-    \draw (db) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (eb);
-    \draw (db) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (eb);
+    \draw (db) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (eb);
+    \draw (db) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (eb);
 
-    \draw (dc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ec);
-    \draw (dc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ec);
+    \draw (dc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (ec);
+    \draw (dc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ec);
 
-    \draw (ellipsisd1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(a)}$} (ellipsise1);
-    \draw (ellipsisd1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsise1);
+    \draw (ellipsisd1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(a)}$} (ellipsise1);
+    \draw (ellipsisd1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsise1);
 
-    \draw (dk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ek);
-    \draw (dk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ek);
+    \draw (dk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (ek);
+    \draw (dk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ek);
 
-    \draw (ellipsisd2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ellipsise2);
-    \draw (ellipsisd2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsise2);
+    \draw (ellipsisd2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (ellipsise2);
+    \draw (ellipsisd2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsise2);
 
-    \draw (dz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(b)}$} (ez);
-    \draw (dz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ez);
+    \draw (dz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(b)}$} (ez);
+    \draw (dz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ez);
     % Sixth row--------------------------------------
@@
     % On Row:
-    \draw (fa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fb);
-    \draw (fa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fb);
+    \draw (fa) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(c)}$} (fb);
+    \draw (fa) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (fb);
 
-    \draw (fb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fc);
-    \draw (fb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fc);
+    \draw (fb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(c)}$} (fc);
+    \draw (fb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (fc);
 
-    \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (ellipsisf1);
-    \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisf1);
+    \draw (fc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(c)}$} (ellipsisf1);
+    \draw (fc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisf1);
 
-    \draw (ellipsisf1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(c)}$} (fk);
-    \draw (ellipsisf1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fk);
+    \draw (ellipsisf1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(c)}$} (fk);
+    \draw (ellipsisf1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (fk);
 
-    \draw (fk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisf2);
-    \draw (fk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisf2);
+    \draw (fk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (ellipsisf2);
+    \draw (fk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisf2);
 
-    \draw (ellipsisf2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (fz);
-    \draw (ellipsisf2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (fz);
+    \draw (ellipsisf2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (fz);
+    \draw (ellipsisf2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (fz);
     % With previous row:
-    \draw (ea) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fa);
-    \draw (ea) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fa);
+    \draw (ea) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(c)}$} (fa);
+    \draw (ea) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (fa);
 
-    \draw (eb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fb);
-    \draw (eb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fb);
+    \draw (eb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(c)}$} (fb);
+    \draw (eb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (fb);
 
-    \draw (ec) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (fc);
-    \draw (ec) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fc);
+    \draw (ec) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(c)}$} (fc);
+    \draw (ec) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (fc);
 
-    \draw (ellipsise1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisf1);
-    \draw (ellipsise1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisf1);
+    \draw (ellipsise1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(c)}$} (ellipsisf1);
+    \draw (ellipsise1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisf1);
 
-    \draw (ek) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (fk);
-    \draw (ek) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fk);
+    \draw (ek) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(d)}$} (fk);
+    \draw (ek) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (fk);
 
-    \draw (ellipsise2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisf2);
-    \draw (ellipsise2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisf2);
+    \draw (ellipsise2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(d)}$} (ellipsisf2);
+    \draw (ellipsise2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisf2);
 
-    \draw (ez) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (fz);
-    \draw (ez) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (fz);
+    \draw (ez) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(d)}$} (fz);
+    \draw (ez) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (fz);
     % Final row--------------------------------------
-    \node (za) [state] at (0,-18) {$(c_{\NH},0)$};
-    \node (zb) [state] at ($(za) + (3,0)$) {$(c_{\NH},1)$};
-    \node (zc) [state] at ($(zb) + (3,0)$) {$(c_{\NH},2)$};
+    \node (za) [state] at (0,-18) {$(c_{2},0)$};
+    \node (zb) [state] at ($(za) + (3,0)$) {$(c_{2},1)$};
+    \node (zc) [state] at ($(zb) + (3,0)$) {$(c_{2},2)$};
     \node (ellipsisz1) at ($(zc) + (3,0)$) {$\dots$};
-    \node(zk) [state] at ($(ellipsisz1) + (3,0)$) {$(c_{\NH},K_{\RG})$};
+    \node(zk) [state] at ($(ellipsisz1) + (3,0)$) {$(c_{2},K_{1})$};
     \node (ellipsisz2) at ($(zk) + (3,0)$) {$\dots$};
-    \node(zz) [state] at ($(ellipsisz2) + (3,0)$) {$(c_{\NH},c_{\RG})$};
+    \node(zz) [state] at ($(ellipsisz2) + (3,0)$) {$(c_{2},c_{1})$};
     % Transitions -----------------------------------
     % On Row:
-    \draw (za) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zb);
-    \draw (za) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zb);
+    \draw (za) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (zb);
+    \draw (za) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (zb);
 
-    \draw (zb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zc);
-    \draw (zb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zc);
+    \draw (zb) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (zc);
+    \draw (zb) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (zc);
 
-    \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz1);
-    \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisz1);
+    \draw (zc) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (ellipsisz1);
+    \draw (zc) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisz1);
 
-    \draw (ellipsisz1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zk);
-    \draw (ellipsisz1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zk);
+    \draw (ellipsisz1) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (zk);
+    \draw (ellipsisz1) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (zk);
 
-    \draw (zk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (ellipsisz2);
-    \draw (zk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (ellipsisz2);
+    \draw (zk) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (ellipsisz2);
+    \draw (zk) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (ellipsisz2);
 
-    \draw (ellipsisz2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{\RG}^{(d)}$} (zz);
-    \draw (ellipsisz2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{\RG}$} (zz);
+    \draw (ellipsisz2) edge[out=45,in=135,->,thick] node [above] {\tiny$\lambda_{1}^{(d)}$} (zz);
+    \draw (ellipsisz2) edge[out=-45,in=-135,<-,thick] node [below] {\tiny$\mu_{1}$} (zz);
     % With previous row:
-    \draw (fa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (za);
-    \draw (fa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (za);
+    \draw (fa) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(c)}$} (za);
+    \draw (fa) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (za);
 
-    \draw (fb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zb);
-    \draw (fb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zb);
+    \draw (fb) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(c)}$} (zb);
+    \draw (fb) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (zb);
 
-    \draw (fc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (zc);
-    \draw (fc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zc);
+    \draw (fc) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(c)}$} (zc);
+    \draw (fc) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (zc);
 
-    \draw (ellipsisf1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(c)}$} (ellipsisz1);
-    \draw (ellipsisf1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisz1);
+    \draw (ellipsisf1) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(c)}$} (ellipsisz1);
+    \draw (ellipsisf1) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisz1);
 
-    \draw (fk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zk);
-    \draw (fk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zk);
+    \draw (fk) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(d)}$} (zk);
+    \draw (fk) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (zk);
 
-    \draw (ellipsisf2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (ellipsisz2);
-    \draw (ellipsisf2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (ellipsisz2);
+    \draw (ellipsisf2) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(d)}$} (ellipsisz2);
+    \draw (ellipsisf2) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (ellipsisz2);
 
-    \draw (fz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{\NH}^{(d)}$} (zz);
-    \draw (fz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{\NH}$} (zz);
+    \draw (fz) edge[out=-125,in=125,->,thick] node [left] {\tiny$\lambda_{2}^{(d)}$} (zz);
+    \draw (fz) edge[out=-55,in=55,<-,thick] node [right] {\tiny$\mu_{2}$} (zz);
 

### 2014-05-13 paper.tex
Section 2 done

@@
 
-\author{
-\name{Paul Harper}
-\institute{Cardiff University}
-\iaddress{Cardiff, UK}
-\email{harper@cf.ac.uk}
-}
-
-\author{
-\name{Jeff Griffiths}
-\institute{Cardiff University}
-\iaddress{Cardiff, UK}
-\email{griffiths@cf.ac.uk}
-}
-
-\author{
-\name{Izabela Komenda}
-\institute{Cardiff University}
-\iaddress{Cardiff, UK}
-\email{komendai@cf.ac.uk}
-}
-
-\author{
-\name{Rob Shone}
-\institute{Cardiff University}
-\iaddress{Cardiff, UK}
-\email{shoner@cf.ac.uk}
-}
+%\author{
+%\name{Paul Harper}
+%\institute{Cardiff University}
+%\iaddress{Cardiff, UK}
+%\email{harper@cf.ac.uk}
+%}
+%
+%\author{
+%\name{Jeff Griffiths}
+%\institute{Cardiff University}
+%\iaddress{Cardiff, UK}
+%\email{griffiths@cf.ac.uk}
+%}
+%
+%\author{
+%\name{Izabela Komenda}
+%\institute{Cardiff University}
+%\iaddress{Cardiff, UK}
+%\email{komendai@cf.ac.uk}
+%}
+%
+%\author{
+%\name{Rob Shone}
+%\institute{Cardiff University}
+%\iaddress{Cardiff, UK}
+%\email{shoner@cf.ac.uk}
+%}
 
@@
 
-In ...
-The main proposition of the work requested by the ABUHB was to develop a mathematical model of bed occupancies at the CCUs at RG and NH.
-After an initial analysis of the data, behavioural aspects became apparent; for example, delaying patients discharge if there was no pressure on CCU beds, or admitting fewer patients if bed occupancy levels were high.
-As a result of this, a state-dependent queueing model has been developed, which includes the dependency of admission rate on actual occupancy \cite{Komenda2013}.
-This state dependent model was applied to both NH and RG separately.
-It is however obvious that the actions of one CCU impact on the other CCU, as diversion of patients from one CCU to the other sometimes occurs.
-A pictorial representation of the situation is given in Figure \ref{diagramofdiversion}.
+In \cite{knight2014} a normal form game consideration of this situation is given akin to the work on EDs in \cite{Deo2011}.
+
+A pictorial representation of the situation considered is given in Figure \ref{diagramofdiversion} where each CCU can choose a capacity threshold at which to divert patients.
 
@@
 \begin{tikzpicture}
-\node (A) at (0,0) [draw] {RG};
-\node (B) at (2,0) [draw] {NH};
+\node (A) at (0,0) [draw] {1};
+\node (B) at (2,0) [draw] {2};
 \draw [->] (-1,0) -- (A);
@@
 
-The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{\NH,\RG\}$. Note that $0\leq K_h\leq c_h$.
+The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{1,2\}$, once diverted the arrival rate is modified as shown in Figure \ref{arrivalrateregions}. Note that $0\leq K_h\leq c_h$.
 
@@
         \draw [dashed, red, thick] (3,0) -- (3,3);
-        \node at (-.5,1) {$K_{\NH}$};
-        \node at (3,3.25) {$K_{\RG}$};
+        \node at (-.5,1) {$K_{1}$};
+        \node at (3,3.25) {$K_{2}$};
         \node at (1.5,2) {$\lambda_{h}^{(a)}$};
@@
     \end{tikzpicture}
-\caption{General arrival rates for each CCU at each region, where $h\in\{\NH, \RG\}$} \label{arrivalrateregions}
+\caption{General arrival rates for each CCU at each region, where $h\in\{1, 2\}$} \label{arrivalrateregions}
 \end{center}
@@
 Throughput of patients is a natural choice of utility given that most hospitals are financially rewarded per served patient \cite{Pate2009}.
-For each threshold pair $(K_{\NH},K_{\RG})$, the utilisation rate $U_h$ and throughput $T_h$ can easily be obtained for each CCU: $h\in\{\text{NH},\text{RG}\}$, using the following formulas:
+For each threshold pair $(K_{1},K_{2})$, the utilisation rate $U_h$ and throughput $T_h$ can easily be obtained for each CCU: $h\in\{\text{1},\text{2}\}$, using the following formulas:
 
@@
 
-where $P^{(h)}=P^{(h)}(K_{\NH},K_{\RG})$ is the steady state probability distribution function (obtained from the corresponding transition matrix $Q=Q(K_{\NH},K_{\RG})$) for $h\in\{\text{NH},\text{RG}\}$.
+where $P^{(h)}=P^{(h)}(K_{1},K_{2})$ is the steady state probability distribution function (obtained from by analysing the Markov chain of Figure \ref{mc}).
 
-For $c_{\NH}=8$, $c_{\RG}=16$, $\lambda_{\NH}=(\lambda_{\NH}^{(a)},\lambda_{\NH}^{(b)},\lambda_{\NH}^{(c)},\lambda_{\NH}^{(d)})=(1.5,3.74,0,0)$, $\lambda_{\RG}=(\lambda_{\RG}^{(a)},\lambda_{\RG}^{(b)},\lambda_{\RG}^{(c)},\lambda_{\RG}^{(d)})=(2.24,0,3.74,0)$ and $(K_{\NH},K_{\RG})=(6,12)$, the steady state probabilities for each CCU are given in Figure \ref{steady_state_probs}.
+The optimisation problem faced by each hospital that gives rise to the game is shown in Figure \ref{model1}.
 
 \begin{figure}[!htbp]
-\hspace{2cm}For all $h\in\{\text{NH}, \text{RG}\}$ minimise:
+\hspace{2cm}For all $h\in\{\text{1}, \text{2}\}$ minimise:
 $$\left(U_{h}-t\right)^2$$
@@
 As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABUHB, long term threshold policies are a realistic consideration.
+In \cite{Knight2014} theoretical results are proved that guarentee pure strategy Nash equilibria in certain cases.
 
-The following result is a sufficient condition for the existence of an equilibrium:\\
-
-\textbf{Theorem.}
-
-Let $f_{h}(k):[1,c_{\bar h}]\to[1,c_h]$ be the best response of player $h\in\{\NH, \RG\}$ to the diversion threshold of $\bar h\ne h$ ($\bar h\in\{\NH, \RG\}$).
-
-If $f_{h}(k)$ is a non-decreasing function in $k$ then the game of Figure \ref{model1} has at least one Nash Equilibrium.
-
-\textbf{proof}
-
-The function $f_h$ is well defined as it maximises a continuous function over a finite discrete set (in case of multiple values that minimize $U_h$, it is assumed that $f_h$ returns the lowest such value).
-
-As such if $f_h$ is non-decreasing then it is in fact a stepwise non-decreasing function.
-If we consider $f_{\NH}$ and $f_{\RG}$ plotted on the same axis (so that the domain of $f_{\NH}$ is the $x$-axis and the domain of $f_{\RG}$ is the y-axis) it is obvious to see that the functions must intersect at some point as shown in Figure \ref{exampleforproof}.
-
-\begin{figure}[!htbp]
-$$\begin{array}{cc}
-\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_NH.pdf}&
-\includegraphics[width=.5\textwidth]{./Images/best_responses_ex_for_proof_RG.pdf}
-\end{array}$$
-\caption{Plots of $f_{\NH}(K_{\RG})$ and $f_{\RG}(K_{\NH})$}\label{exampleforproof}
-\end{figure}
-
-This point of intersection corresponds to a Nash Equilibrium of Figure \ref{model1}.
-$\square$
+Using this and structural properties of the problem a Nash equilibria can be found.
+A variety of numerical results are shown giving the PoA for various scenarios but importantly this module can aid in the informed assignment of a policy $t$.
+Figure \ref{mintargetvdemandmodel2} show the smallest value of $t$ that gives a PoA for a variation of demand ($x=0$ corresponds to the actual demand of the system in consideration).
+We see that a value of $t=.72$ is sensible in our model.
 

### 2014-05-14 paper.tex
Finished conclusion

@@
 \begin{abstract}
+
 Individual behaviour has an effect on the optimal control of queueing systems.
@@
 \section{Introduction}
+
+The best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{Roth}.
+This work uses matching game algorithms to match medical interns to hospitals.
+The purpose of this paper is to discuss some work relevant to congestion and healthcare.
 
@@
 As such a Nash Equilibrium is not guaranteed by traditional game theoretical results \cite{Nash1950}, but based on discussions with ABUHB, long term threshold policies are a realistic consideration.
-In \cite{Knight2014} theoretical results are proved that guarentee pure strategy Nash equilibria in certain cases.
+In \cite{knight2014} theoretical results are proved that guarentee pure strategy Nash equilibria in certain cases.
 
@@
 
+In this manuscript two game theoretic environments applied to healthcare have been considered:
+
 \begin{itemize}
-    \item Describe potential
-    \item Describe further work
-    \item Discuss potential for heuristic approaches
+    \item Modelling choices of patients;
+    \item Modelling choices of managers.
 \end{itemize}
+
+The effect of stochasticity in healthcare systems is well understood and there is a wealth of research to match this.
+The effect of individual behaviour is less understood.
+Game theory and Price of Anarchy analysis offers one way to measure this effect.
+
+Importantly, here are a variety of further avenues for this exciting area of research:
+
+\begin{itemize}
+    \item Games involving players from different parts of a hospital and/or multiple hospitals;
+    \item Machine loading games which can be applied to scheduling tasks;
+    \item Further policy informing work.
+\end{itemize}
+
+With regards to methodological approaches there are a variety of tools available.
+
+Firstly, one can model particular systems with parameters corresponding to the strategies of players (similar to the work described in Section \cite{sec:managinghospitals}).
+Secondly, there are specific game theoretic models that can be applied directly to healthcare systems (similar to the work described in Section \cite{sec:choosingqueues}).
+Finally there are also a variety of novel approaches that can be used such as using evolutionary game theoretic models.
+Specific heuristic approaches relevant to Markov Decision Process in both optimal and selfish calculations offer interesting avenues for research.
+
+The fact that optimal behaviour and selfish behaviour are two sides of the same coin is well understood in unobservable queues.
+Finding similar connections in observable queues is an open research problem.
 

### 2014-05-14 paper.tex
Changed title thing
Fixed abstract

@@
 
-\title{An Incomplete Overview of some Applications of Game Theory to Patient Flow}
+\title{An Incomplete Overview of Some Applications of Game Theory to Patient Flow}
 
@@
 
-Individual behaviour has an effect on the optimal control of queueing systems.
-This idea sits at the intersection of queueing theory and game theory.
+Individual behaviour has an effect on the optimal control of queueing systems, which is an idea that sits at the intersection of queueing theory and game theory.
 The role of this paper is to discuss some work in this area applied to healthcare systems.
@@
 A second aspect is the effect that managers may have when acting rationally in their control of queueing systems.
+
+Thoughts for future directions of work are also considered.
 \end{abstract}
@@
 \end{center}
-\caption{Routing game $m$ hospitals to $n$ services.}\label{fig:routinggame}
+\caption{Routing game: $m$ hospitals to $n$ services.}\label{fig:routinggame}
 \end{figure}

### 2014-05-14 paper.tex
Happy with introduction

@@
 This work uses matching game algorithms to match medical interns to hospitals.
-The purpose of this paper is to discuss some work relevant to congestion and healthcare.
+The purpose of this paper is to discuss some work relevant to a different area of healthcare: congestion.
 
@@
 In \cite{Adler1969,Bell1983,Edelson1971,Knudsen1972,Luski1976,Naor1969,Yechiali1972} a variety of models are discussed that obtain optimal and equilibrium behaviour in situations where individuals can choose between a best queue to join.
-Most of the work considers these systems in a theoretical context.
+Most of the work considers these systems in a theoretical context but often comes to a common conclusion:
+
+\begin{center}
+\textit{Selfish users make busier systems.}
+\end{center}
 
@@
 The degree of central control that should be exercised is a very important question to be considered by governments and/or policy makers.
-What is the effect of allowing individuals to choose service provider?
+How do we measure the effect of selfish behaviour?
 
 This is a question that is answered using the Game theoretical concept referred to as the \textit{Price of Anarchy} (PoA).
-This was first defined in \cite{Koutsoupias2009} but an excellent introduction is given in \cite{Roughgarden2005}.
+This was first defined in \cite{Koutsoupias2009} but an excellent overview is given in \cite{Roughgarden2005}.
 The PoA is defined as the ratio of the selfish utility to the optimal utility.
 
-Section \label{sec:choosingqueues} will discuss some PoA analysis applied to individuals choosing between queues.
-Section \label{sec:managingqueues} will discuss similar analysis in the case of selfish behaviour related to the management of queues.
-Section \label{sec:conclusion} will conclude with a summary and thoughts for further work.
+Section \ref{sec:choosingqueues} will discuss some PoA analysis applied to individuals choosing between queues.
+Section \ref{sec:managingqueues} will discuss similar analysis in the case of selfish behaviour related to the management of queues.
+Section \ref{sec:conclusion} will conclude with a summary and thoughts for further work.
 

### 2014-05-14 paper.tex
Happy with First section - still need to draw new pictures

@@
 
-This section describes how patient choices between various congestion affected services may be modelled.
+This section describes how patient choices between various congestion affected service centres may be modelled.
 In particular the situation shown diagrammatically in Figure \ref{fig:choices} is considered: patients have a choice amongst $M/M/c$ queues.
-Each $M/M/c$ queue corresponds to a (simple) model of a Hospital (or indeed any other public service facility).
+Each $M/M/c$ queue corresponds to a (simple) model of a hospital (or indeed any other public service facility).
 
@@
 
-There are two approaches to solving this problem: assuming that patients observe or not the system states before choosing a facility.
-A rigorous comparison of these two approaches for individuals choosing to join an $M/M/1$ queue is given in \cite{shone2013comparisons}.
+There are two approaches to modelling this situation: assuming that patients observe or not the system state before choosing a facility.
+A rigorous comparison of these two approaches for individuals choosing to join(or not) an $M/M/1$ queue is given in \cite{shone2013comparisons}.
 
 An unobservable study is given in \cite{Knight2013} where routing games \cite{Roughgarden2005} are used to study the system described.
-The routing game used is shown in \ref{fig:routinggame}.
+The routing game used is shown in Figure \ref{fig:routinggame}.
 
@@
 
-To be able to obtain the PoA for a given instance the following mathematical program must be solved:
+As a utility function $w_i$ is taken to be the mean waiting time in an $M/M/c$ queue.
+From known results on convexity of this measure \cite{} the following optimisation problems can be solved straightforwardly so as to be able to obtain the PoA for a given instance:
 
@@
 The profile of Figure \ref{fig:poaprofile} is shown to hold in general.
+A system under very high or very low demand will not suffer greatly from the removal of central control.
+Most public service systems are however built to match demand which implies a large PoA.
 
@@
 
-Further to the theoretical consideration the PoA was calculated for a large case study using Hospital in Wales offering knee surgeries.
-A high PoA was calculated for the current demand.
+Further to the theoretical consideration the PoA was calculated for a large case study using Hospital in Wales offering knee surgeries and a high PoA was calculated for the current demand which verifies the previous observation.
 
-To consider systems where individuals are able to observe the system there are two approaches: the first is to use a simulation based approach that allows individuals to choose their most desirable queue.
-One such approach that was considered specifically in the context of healthcare was considered in \cite{Knight2010}.
+To consider systems where individuals are able to observe the system (before making a decision) there are two approaches: the first is to use a simulation based approach that allows individuals to choose their most desirable queue.
+One such piece of work that was considered specifically in the context of healthcare is \cite{Knight2010}.
 
 Given that individuals will consider a simple selfish decision rule this approach is relatively straightforward and can also be considered using straightforward analytical Markov models.
-The difficulty with this approach is appears when attempting to obtain the PoA.
+The difficulty with this approach appears when attempting to obtain the PoA which requires an optimal routing decision.
 
-In \cite{Shone2014} various dynamic programming and approximate dynamic programming techniques are proposed that are able to not only give an optimal policy but also prove the following observation:
+In \cite{Shone2014} various dynamic programming and approximate dynamic programming techniques are proposed that are able to not only give an optimal policy but also prove the following observation holds once again:
 

### 2014-05-14 paper.tex
Checked through conclusion and second section

@@
 
-\begin{figure}[!hbtp]
+\begin{table}[!hbtp]
 \begin{center}
@@
 \end{center}
-\end{figure}
+\end{table}
 
@@
 
-Following the analysis of two critical care units (CCUs) it was found that the only a state dependent queueing model (where the demand rate to each CCU depended on the state of the CCU) would give a valid representation of the system.
-Upon discussion with the managers in question, it was acknowledged that certain behaviours took place.
+Following recent analysis of two critical care units (CCUs) it was found that only a state dependent queueing model (where the demand rate to each CCU depended on the state of the CCU) would give a valid representation of the system.
+Upon discussion with the CCU managers in question, it was acknowledged that certain behavioural control of admissions occurred, even if it was at a subconscious level.
 Indeed when one CCU was at high capacity it was likely to divert patients to the other CCU.
@@
 In \cite{knight2014} a normal form game consideration of this situation is given akin to the work on EDs in \cite{Deo2011}.
-
-A pictorial representation of the situation considered is given in Figure \ref{diagramofdiversion} where each CCU can choose a capacity threshold at which to divert patients.
+A pictorial representation of the situation considered is given in Figure \ref{diagramofdiversion} where each CCU can choose a capacity threshold at which to divert patients, and Table \ref{tab:parameters1} shows the parameters used.
 
@@
 
-The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{1,2\}$, once diverted the arrival rate is modified as shown in Figure \ref{arrivalrateregions}. Note that $0\leq K_h\leq c_h$.
+\begin{table}[!hbtp]
+\begin{center}
+\begin{tabular}{cl}
+\toprule
+Parameter & Interpretation\\
+\midrule
+$m\in\mathbb{Z}$& Number of sources\\
+$n\in\mathbb{Z}$& Number of service centers\\
+$\beta\in\mathbb{R}_{\geq 0}^{m}$& Worth of service\\
+$\Lambda\in\mathbb{R}_{\geq 0}^{m}$& Demand rate\\
+$w_j$ for $j\in[n]$& A convex utility function\\
+$d_{ij}$ for $i\in[m],\;j\in[n]$& Distance from source $i$ to service center $j$\\
+$\lambda_{ij}$ for $i\in[m],\;j\in[n]$& Traffic from source $i$ to service center $j$\\
+\toprule
+\end{tabular}
+\caption{Parameters of model}\label{tab:parameters1}
+\end{center}
+\end{table}
+
+The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{1,2\}$, once diverted the arrival rate is modified as shown in Figure \ref{arrivalrateregions}.
+In general it is assumed that $\lambda_h^{(a)}\geq \lambda_{h}^{(b)}, \lambda_{h}^{(c)}\geq \lambda_{h}^{(d)}$ (so that setting a diversion threshold implies a reduction of patient flow).
+Note that $0\leq K_h\leq c_h$.
 
@@
 
-Utilities will be of interest when this queueing theoretical model will be inserted in the game theoretical model.
-Throughput of patients is a natural choice of utility given that most hospitals are financially rewarded per served patient \cite{Pate2009}.
+Throughput of patients is a natural choice of utility for the game theoretic model given that most hospitals are financially rewarded per served patient \cite{Pate2009}.
 For each threshold pair $(K_{1},K_{2})$, the utilisation rate $U_h$ and throughput $T_h$ can easily be obtained for each CCU: $h\in\{\text{1},\text{2}\}$, using the following formulas:
@@
 
-The optimisation problem faced by each hospital that gives rise to the game is shown in Figure \ref{model1}.
+The optimisation problem faced by each hospital that gives rise to the game is:
 
-\begin{figure}[!htbp]
-\hspace{2cm}For all $h\in\{\text{1}, \text{2}\}$ minimise:
-$$\left(U_{h}-t\right)^2$$
-\hspace{2cm}Subject to:
-\begin{align}
-0\leq & K_h \leq c_{h}\nonumber\\
-&K_h \in  \mathbb{Z}\nonumber
-\end{align}
-\caption{The optimisation problem underlying the game}\label{model1}
-\end{figure}
+For all $h\in\{\text{1}, \text{2}\}$ minimise:
+\begin{equation}\left(U_{h}-t\right)^2\end{equation}
+Subject to:
+\begin{equation}
+0\leq K_h \leq c_{h}
+\end{equation}
+\begin{equation}
+K_h \in  \mathbb{Z}
+\end{equation}
 
@@
 Figure \ref{mintargetvdemandmodel2} show the smallest value of $t$ that gives a PoA for a variation of demand ($x=0$ corresponds to the actual demand of the system in consideration).
-We see that a value of $t=.72$ is sensible in our model.
+This value was obtained in a model where CCUs could divert demand unless both CCUs are in diversion in which case CCUs must deal with their own demand.
 
@@
 
+We see that a value of $t=.72$ is recommended for the actual demand of the system.
+While this value does not necessarily give an exact value worth installing as policy the methodology gives a valid approach to indicating a sensible target.
+Furthermore, as demand increases, we see that the recommended target value increases so as to align the goals of the facilities align with the goals of the overall system.
+
 \section{Conclusions}\label{sec:conclusion}
 
-In this manuscript two game theoretic environments applied to healthcare have been considered:
+In this manuscript two game theoretic models applied to healthcare have been considered:
 
@@
 
-Importantly, here are a variety of further avenues for this exciting area of research:
+Importantly, there are a variety of further avenues for this exciting area of research:
 
@@
 With regards to methodological approaches there are a variety of tools available.
-
-Firstly, one can model particular systems with parameters corresponding to the strategies of players (similar to the work described in Section \cite{sec:managinghospitals}).
-Secondly, there are specific game theoretic models that can be applied directly to healthcare systems (similar to the work described in Section \cite{sec:choosingqueues}).
+Firstly, one can model particular systems with parameters corresponding to the strategies of players (similar to the work described in Section \ref{sec:managingqueues}).
+Secondly, there are specific game theoretic models that can be applied directly to healthcare systems (similar to the work described in Section \ref{sec:choosingqueues}).
 Finally there are also a variety of novel approaches that can be used such as using evolutionary game theoretic models.

### 2014-05-14 paper.tex
Have table for second section

@@
 \end{tabular}
-\caption{Parameters of model}\label{tab:parameters}
+\caption{Parameters of choice model}\label{tab:parameters}
 \end{center}
@@
 \midrule
-$m\in\mathbb{Z}$& Number of sources\\
-$n\in\mathbb{Z}$& Number of service centers\\
-$\beta\in\mathbb{R}_{\geq 0}^{m}$& Worth of service\\
-$\Lambda\in\mathbb{R}_{\geq 0}^{m}$& Demand rate\\
-$w_j$ for $j\in[n]$& A convex utility function\\
-$d_{ij}$ for $i\in[m],\;j\in[n]$& Distance from source $i$ to service center $j$\\
-$\lambda_{ij}$ for $i\in[m],\;j\in[n]$& Traffic from source $i$ to service center $j$\\
+$h\in\{1,2\}$& CCU\\
+$c_h$& Capacity of CCU\\
+$K_h$& Cutoff strategy of CCU\\
+$\lambda_{h}^{\text{area}}$& Demand rate as described in Figure \ref{arrivalrateregions}\\
+$\mu_{h}$&Service rate of CCU\\
 \toprule
 \end{tabular}
-\caption{Parameters of model}\label{tab:parameters1}
+\caption{Parameters of CCU model}\label{tab:parameters1}
 \end{center}

### 2014-05-14 paper.tex
Replaced tikz version of first FIGURA

@@
 
-The best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{Roth}.
+The best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{roth_redesign_1999}.
 This work uses matching game algorithms to match medical interns to hospitals.
@@
 \begin{center}
-\includegraphics[width=.7\textwidth]{./Images/Hospital_Choices.pdf}
+
+\begin{tikzpicture}
+\node (S1) at (0,0) [circle, draw=blue, fill=blue!5] {$\Lambda_1$};
+\node (S2) at (0,-2) [circle, draw=blue, fill=blue!5] {$\Lambda_2$};
+\node (S3) at (0,-4)  {$\vdots$};
+\node (S4) at (0,-6) [circle, draw=blue, fill=blue!5] {$\Lambda_m$};
+
+\node (B1) at (-5,0) [circle, draw=blue, fill=red!5] {$\beta_1$};
+\node (B2) at (-5,-2) [circle, draw=blue, fill=red!5] {$\beta_2$};
+\node (B3) at (-5,-4)  {$\vdots$};
+\node (B4) at (-5,-6) [circle, draw=blue, fill=red!5] {$\beta_m$};
+
+\node (F1) at (5,-1) [circle, draw=blue, fill=red!5] {$w_1$};
+\node (F3) at (5,-3)  {$\vdots$};
+\node (F2) at (5,-5) [circle, draw=blue, fill=red!5] {$w_n$};
+
+\draw [->, red] (S1) -- (B1);
+\draw [->, red] (S2) -- (B2);
+\draw [->, red] (S4) -- (B4);
+
+\draw [->, red] (S1) -- (F1) node [midway, above, sloped, black] (TextNode) {$\lambda_{11}$};
+\draw [->, red] (S1) -- (F2) node [midway, above, sloped, black] (TextNode) {$\lambda_{1n}$};
+\draw [->, red] (S2) -- (F1) node [midway, above, sloped, black] (TextNode) {$\lambda_{21}$};
+\draw [->, red] (S2) -- (F2) node [near start, above, sloped, black] (TextNode) {$\lambda_{2n}$};
+\draw [->, red] (S4) -- (F1) node [near start, above, sloped, black] (TextNode) {$\lambda_{m1}$};
+\draw [->, red] (S4) -- (F2) node [midway, above, sloped, black] (TextNode) {$\lambda_{mn}$};
+
+\node at (-2.5,-7) {Balk};
+\node at (2.5,-7) {Seek Service};
+\end{tikzpicture}
 \end{center}
@@
 As a utility function $w_i$ is taken to be the mean waiting time in an $M/M/c$ queue.
-From known results on convexity of this measure \cite{} the following optimisation problems can be solved straightforwardly so as to be able to obtain the PoA for a given instance:
+From known results on convexity of this measure \cite{lee_note_1983} the following optimisation problems can be solved straightforwardly so as to be able to obtain the PoA for a given instance:
 

### 2014-05-14 paper.tex
Have drawn routing game in tikz

@@
 \begin{center}
-\includegraphics[width=.7\textwidth]{./Images/Hospital_Routing_Game.pdf}
+
+\begin{tikzpicture}
+\node (S1) at (0,0) [circle, draw=blue, fill=blue!5] {} node[left=.1cm] {$\Lambda_1$};
+\node (S2) at (0,-2) [circle, draw=blue, fill=blue!5] {} node at (S2)[left=.1cm] {$\Lambda_2$};
+\node (S3) at (0,-4)  {$\vdots$};
+\node (S4) at (0,-6) [circle, draw=blue, fill=blue!5] {} node at (S4) [left=.1cm] {$\Lambda_m$};
+
+\node (E) at (10,-3) [circle, draw=blue, fill=red!5] {};
+
+\node (F1) at (5,-1) [circle, draw=blue, fill=red!5] {};
+\node (F3) at (5,-3)  {$\vdots$};
+\node (F2) at (5,-5) [circle, draw=blue, fill=red!5] {};
+
+\draw [->, red] (F1) -- (E) node [midway, above, sloped, black] (TextNode) {$w_{1}$};
+\draw [->, red] (F2) -- (E) node [midway, above, sloped, black] (TextNode) {$w_{n}$};
+
+\draw [->, red] (S1) -- (F1) node [midway, above, sloped, black] (TextNode) {$d_{11}$};
+\draw [->, red] (S1) -- (F2) node [midway, above, sloped, black] (TextNode) {$d_{1n}$};
+\draw [->, red] (S2) -- (F1) node [midway, above, sloped, black] (TextNode) {$d_{21}$};
+\draw [->, red] (S2) -- (F2) node [near start, above, sloped, black] (TextNode) {$d_{2n}$};
+\draw [->, red] (S4) -- (F1) node [near start, above, sloped, black] (TextNode) {$d_{m1}$};
+\draw [->, red] (S4) -- (F2) node [midway, above, sloped, black] (TextNode) {$d_{mn}$};
+
+\draw [->, red] (S1) edge[out=45, in=135] node [above, black] {$\beta_1$} (E);
+\draw [->, red] (S4) edge[out=-45, in=-135] node [above, black] {$\beta_m$} (E);
+\draw [->, red] (S2) edge[out=100, in=135] node [above, black] {$\beta_2$} (E);
+
+\end{tikzpicture}
 \end{center}

### 2014-05-14 paper.tex
Everything fitting nice
Have resized better
Paper checked

@@
 
-The best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{roth_redesign_1999}.
-This work uses matching game algorithms to match medical interns to hospitals.
-The purpose of this paper is to discuss some work relevant to a different area of healthcare: congestion.
+Arguably, the best known work applying Game Theory to Healthcare is Roth's Noble prize winning work \cite{roth_redesign_1999}.
+This work uses matching game algorithms to assign medical interns to hospitals.
+The purpose of the present manuscript is to discuss some work relevant to a different area of healthcare: congestion.
 
@@
 In \cite{Adler1969,Bell1983,Edelson1971,Knudsen1972,Luski1976,Naor1969,Yechiali1972} a variety of models are discussed that obtain optimal and equilibrium behaviour in situations where individuals can choose between a best queue to join.
-Most of the work considers these systems in a theoretical context but often comes to a common conclusion:
+Most of the cited papers consider these systems in a theoretical context but most come to a common conclusion:
 
@@
 
-Most research where game theory is applied in healthcare has mainly concentrated on Emergency Departments (EDs) and how to deal with diversions of patients and ambulances.
-In \cite{Hagtvedt2009} cooperative strategies for hospitals are considered, in order to reduce occurrences when ambulances are turned away due to the ED being full.
+Research where game theory and queueing theory is applied to healthcare has mainly concentrated on Emergency Departments (EDs) and how to deal with diversions of patients and ambulances.
+In \cite{Hagtvedt2009} cooperative strategies for hospitals are considered, in order to reduce occurrences where ambulances are turned away due to the ED being full.
 In \cite{Deo2011} a queueing network model of two EDs is proposed to study the network effect of ambulance diversion.
 Each ED aims to minimise the expected waiting time of its patients (walk-ins and ambulances) and chooses its diversion threshold based on the number of patients at its location.
-Decentralised decision making in the network is modelled as a non-cooperative game.
 
-The degree of central control that should be exercised is a very important question to be considered by governments and/or policy makers.
-How do we measure the effect of selfish behaviour?
+In these settings, how do we measure the effect of selfish behaviour?
 
@@
 Section \ref{sec:managingqueues} will discuss similar analysis in the case of selfish behaviour related to the management of queues.
-Section \ref{sec:conclusion} will conclude with a summary and thoughts for further work.
+Finally, Section \ref{sec:conclusion} will conclude with a summary and thoughts for further work.
 
@@
 
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]
 \node (S1) at (0,0) [circle, draw=blue, fill=blue!5] {$\Lambda_1$};
@@
 
-The parameters of this system are shown in Table \ref{tab:parameters}.
+The parameters of this system are summarised in Table \ref{tab:parameters}.
 
@@
 There are two approaches to modelling this situation: assuming that patients observe or not the system state before choosing a facility.
-A rigorous comparison of these two approaches for individuals choosing to join(or not) an $M/M/1$ queue is given in \cite{shone2013comparisons}.
+A rigorous comparison of these two approaches for individuals choosing to join (or not) an $M/M/1$ queue is given in \cite{shone2013comparisons}.
 
@@
 
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.7, every node/.style={scale=0.7}]
 \node (S1) at (0,0) [circle, draw=blue, fill=blue!5] {} node[left=.1cm] {$\Lambda_1$};
@@
 
-The constant $\alpha_i\in\mathbb{R}_{\geq0}$ is simply a weighting statistic for the relative importance of travel distances to the other factors (once again allowing for this coefficient to be dependent on population partitioning).
+The constant $\alpha_i\in\mathbb{R}_{\geq0}$ is simply a weighting statistic for the relative importance of travel distances to the other factors.
 The Nash flow corresponding to the flow at which all traffic from a given source travels on minimal paths can be shown to be given by the flow that minimises the following function:
@@
 \begin{center}
-\includegraphics[width=.7\textwidth]{./Images/PoAPlotForSimpleDiagram.pdf}
+\begin{tikzpicture}
+
+\draw [->] (0,0) -- (10,0);
+\draw [->] (0,0) -- (0,8);
+\node at (10,0) [below] {$\Lambda$};
+\node at (0,8) [left] {PoA};
+
+%\node (social) at (3,0) [below] {$x^*$};
+%\node (selfish) at (7,0) [below] {$\tilde x$};
+
+\draw [dashed] (3,0) -- (3,8);
+\draw [dashed] (7,0) -- (7,8);
+
+\draw [thick] (0,3) -- (3,3);
+\draw (3,3) edge[thick,out=0,in=-100] (7,6);
+\draw (7,6) edge[thick,out=-80,in=170] (10,4);
+
+\node at (1.5,4) [text width=2cm]{Low level of demand};
+\node at (5,6) {Inefficient system};
+\node at (8.5,2) [text width=2cm]{High level of demand};
+
+\end{tikzpicture}
+
 \end{center}
@@
 
-Further to the theoretical consideration the PoA was calculated for a large case study using Hospital in Wales offering knee surgeries and a high PoA was calculated for the current demand which verifies the previous observation.
+Further to the theoretical consideration the PoA was calculated for a large case study using hospitals in Wales offering knee surgeries and a high PoA was calculated for the current demand which verifies the previous observation.
 
@@
 Following recent analysis of two critical care units (CCUs) it was found that only a state dependent queueing model (where the demand rate to each CCU depended on the state of the CCU) would give a valid representation of the system.
-Upon discussion with the CCU managers in question, it was acknowledged that certain behavioural control of admissions occurred, even if it was at a subconscious level.
+Upon discussion with the CCU managers in question, it was acknowledged that a certain behavioural control of admissions, even if it was at a subconscious level.
 Indeed when one CCU was at high capacity it was likely to divert patients to the other CCU.
@@
 In \cite{knight2014} a normal form game consideration of this situation is given akin to the work on EDs in \cite{Deo2011}.
-A pictorial representation of the situation considered is given in Figure \ref{diagramofdiversion} where each CCU can choose a capacity threshold at which to divert patients, and Table \ref{tab:parameters1} shows the parameters used.
+A pictorial representation of the situation considered is given in Figure \ref{diagramofdiversion} where each CCU can choose a capacity threshold at which to divert patients.
+Table \ref{tab:parameters1} shows the parameters used.
 
@@
 The capacity thresholds are denoted as $K_{h}\in\mathbb{Z}$ for $h\in\{1,2\}$, once diverted the arrival rate is modified as shown in Figure \ref{arrivalrateregions}.
-In general it is assumed that $\lambda_h^{(a)}\geq \lambda_{h}^{(b)}, \lambda_{h}^{(c)}\geq \lambda_{h}^{(d)}$ (so that setting a diversion threshold implies a reduction of patient flow).
+In general it is assumed that setting a diversion threshold implies a reduction of patient flow.
 Note that $0\leq K_h\leq c_h$.
@@
 
-$$U_{h}={{\sum_{n=0}^{c_h} nP^{(h)}(n)}\over{c_{h}}}$$
-$$T_{h}=\mu_h \sum _{n=0}^{c_h} nP^{(h)}(n)$$
+$$U_{h}={{\sum_{n=0}^{c_h} nP^{(h)}_n}\over{c_{h}}}$$
+$$T_{h}=\mu_h \sum _{n=0}^{c_h} nP^{(h)}_n$$
 
@@
 Using this and structural properties of the problem a Nash equilibria can be found.
-A variety of numerical results are shown giving the PoA for various scenarios but importantly this module can aid in the informed assignment of a policy $t$.
-Figure \ref{mintargetvdemandmodel2} show the smallest value of $t$ that gives a PoA for a variation of demand ($x=0$ corresponds to the actual demand of the system in consideration).
+A variety of numerical results are shown giving the PoA for various scenarios but importantly this approach can aid in the informed assignment of a policy $t$.
+For example, figure \ref{mintargetvdemandmodel2} show the smallest value of $t$ that gives a PoA for a variation of demand ($x=0$ corresponds to the actual demand of the system in consideration).
 This value was obtained in a model where CCUs could divert demand unless both CCUs are in diversion in which case CCUs must deal with their own demand.
@@
 We see that a value of $t=.72$ is recommended for the actual demand of the system.
-While this value does not necessarily give an exact value worth installing as policy the methodology gives a valid approach to indicating a sensible target.
+While this value does not necessarily give an exact target worth installing as policy the methodology gives a valid approach to indicating a sensible target.
 Furthermore, as demand increases, we see that the recommended target value increases so as to align the goals of the facilities align with the goals of the overall system.
